\documentclass{tufte-book}

\hypersetup{colorlinks}% uncomment this line if you prefer colored hyperlinks (e.g., for onscreen viewing)

%%
% Book metadata
\title{Cyber Peripherals\thanks{Hamish, Lumpley, Avery and the RPGtalk slackers }}
\author[Cromlyn Games]{Cromlyn Games}
\publisher{Publisher of This Book}

%%
% If they're installed, use Bergamo and Chantilly from www.fontsite.com.
% They're clones of Bembo and Gill Sans, respectively.
%\IfFileExists{bergamo.sty}{\usepackage[osf]{bergamo}}{}% Bembo
%\IfFileExists{chantill.sty}{\usepackage{chantill}}{}% Gill Sans

%\usepackage{microtype}



%%
% Just some sample text
\usepackage{lipsum}

%for fancy lists
\usepackage{tikz}
\usetikzlibrary{shadows}
\newcommand{\mylist}{\tikz[overlay]\draw(-.2,-.2)--(-.2,.4) [path fading=east](-.2,.15)--(.1,.15);} %adds the |- shape to the start of each list item
\newcommand{\mylistend}{\tikz[overlay]\draw(-.2,.15)--(-.2,.4) [path fading=east](-.2,.15)--(.1,.15);} %adds the |- shape to the start of each list item
\newcommand{\myitem}{\item[\mylist]} %defines the scope of the mylist command to be 2nd level sublists
\newcommand{\myitemend}{\item[\mylistend]} %defines the scope of the mylist command to be 2nd level sublists
%\renewcommand\labelitemi{---}  % turns bullets into long dashes

%%
% For nicely typeset tabular material
\usepackage{booktabs}

% to break lists over multi columns
\usepackage{multicol}


%%
% For graphics / images
\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
\graphicspath{{graphics/}}

% The fancyvrb package lets us customize the formatting of verbatim
% environments.  We use a slightly smaller font.
\usepackage{fancyvrb}
\fvset{fontsize=\normalsize}

%%
% Prints argument within hanging parentheses (i.e., parentheses that take
% up no horizontal space).  Useful in tabular environments.
\newcommand{\hangp}[1]{\makebox[0pt][r]{(}#1\makebox[0pt][l]{)}}

%%
% Prints an asterisk that takes up no horizontal space.
% Useful in tabular environments.
\newcommand{\hangstar}{\makebox[0pt][l]{*}}

%%
% Prints a trailing space in a smart way.
\usepackage{xspace}

% Prints the month name (e.g., January) and the year (e.g., 2008)
\newcommand{\monthyear}{%
  \ifcase\month\or January\or February\or March\or April\or May\or June\or
  July\or August\or September\or October\or November\or
  December\fi\space\number\year
}


% Prints an epigraph and speaker in sans serif, all-caps type.
\newcommand{\openepigraph}[2]{%
  %\sffamily\fontsize{14}{16}\selectfont
  \begin{fullwidth}
  \sffamily\large
  \begin{doublespace}
  \noindent\allcaps{#1}\\% epigraph
  \noindent\allcaps{#2}% author
  \end{doublespace}
  \end{fullwidth}
}

% Inserts a blank page
\newcommand{\blankpage}{\newpage\hbox{}\thispagestyle{empty}\newpage}

\usepackage{units}

% Typesets the font size, leading, and measure in the form of 10/12x26 pc.
\newcommand{\measure}[3]{#1/#2$\times$\unit[#3]{pc}}

% Macros for typesetting the documentation

% Generates the index
\usepackage{imakeidx}
%\makeindex[name=moves, title={Index of moves}] % on reflection, not needed. 
\makeindex[name=stuff, title ={Index of elements, items}]
\makeindex % general index for playbooks and stuff

\begin{document}

% Front matter
\frontmatter

% r.1 blank page
\blankpage

% v.2 epigraphs
\newpage\thispagestyle{empty}

\openepigraph{%
Acknowledge up front that the PCs are going to win, and never sweat it. Then use the dice to escalate, escalate, escalate. We all know the PCs are going to win. What will it cost them?
}{Lumpley}
\vfill

\openepigraph{%
A designer knows that he has achieved perfection 
not when there is nothing left to add, 
but when there is nothing left to take away.
}{Antoine de Saint-Exup\'{e}ry}
\vfill
\openepigraph{%
The integrity of its span was rigorous as the modern program itself, yet around this had grown another reality, intent on its own agenda. This had occurred piecemeal, to no set plan, employing every imaginable technique and material. The result was something amorphous, startlingly organic.
}{ William Gibson, Virtual Light}
\vfill




% r.3 full title page
\maketitle


% v.4 copyright page
\newpage
\begin{fullwidth}
~\vfill
\thispagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}
Copyright \copyright\ \the\year\ \thanklessauthor

\par\smallcaps{Published by \thanklesspublisher}

\par\smallcaps{tufte-latex.github.io/tufte-latex/}

\par Licensed under the Apache License, Version 2.0 (the ``License''); you may not
use this file except in compliance with the License. You may obtain a copy
of the License at \url{http://www.apache.org/licenses/LICENSE-2.0}. Unless
required by applicable law or agreed to in writing, software distributed
under the License is distributed on an \smallcaps{``AS IS'' BASIS, WITHOUT
WARRANTIES OR CONDITIONS OF ANY KIND}, either eXpress or implied. See the
License for the specific language governing permissions and limitations
under the License.\index{license}

\par\textit{First printing, \monthyear}
\end{fullwidth}

% r.5 contents
\tableofcontents

\listoffigures

\listoftables

% r.7 dedication
\cleardoublepage
~\vfill
\begin{doublespace}
\noindent\fontsize{18}{22}\selectfont\itshape
\nohyphenation
Dedicated to those who appreciate \LaTeX{} 
and the work of \mbox{Edward R.~Tufte} 
and \mbox{Donald E.~Knuth}.

And to the horde of goblins who died defending them.
\end{doublespace}
\vfill
\vfill


% r.9 introduction
\cleardoublepage
\chapter*{Playing in Cyber\_Peripherals}
\label{ch:playing in Cyber_Peripherals}
Cyber\_Peripherals is a stand alone game of stories for 3-5 players in a cyberpunk world. Most of you will play the roles of neon slumdogs and one of you will be the Master of Ceremonies (MC for short). The game is a conversation between you all, with the MC to facilitate and fill in what is needed for the story. From time to time, the story will reach a point where the outcome is interesting and uncertain. The dice help out here, and add a sense of tension as their fall changes the fictional world and sparks new directions for the conversation.
The story will center around a community of individuals and how they live under the various pressures of a Zaibatsu dominated future. You're unlikely to be pulling off Shadowrun type missions, and if you are, you'll want to take a  look at the rpg The Sprawl, which is built for that. This rpg is designed to be compatible, but is more interested in the kind of stories that came later in the cyberpunk genre, those of Greg Egan or Tricia Sullivan or Nalo Hopkinson. 

In fine cyberpunk tradition, this book is pirated hackjob. Bits of the Sprawl, Urban Shadows and Apocalypse World have been recycled, paired up and duct taped together with Simple World. The playbooks are mostly original, but precious little else is. A favour is owed to the designers, testers and editors of those books.

\section {Why play Cyber\_Peripherals?}
Play if you want to play to find out what happens in a neon and chrome cyberpunk future.
Play if you want to create a story about everyday folk living on the peripheries.
Play if you are playing the Sprawl, and want to follow your Killer character home to see how they do the groceries.
Play if you want to struggle against the Man, in a world where 'Man' needs citation marks.
Play if you want to win sometimes, lose sometimes, and explore the future twenty minutes from now.

\section{How to use this book} \label{sec: how to use this book}
\marginnote{If you're an experienced player or MC of Powered By the Apocalypse type games, you probably want to check the MC  \nameref{sec: agenda}, \nameref{sec: principles} and \nameref{sec: mcmoves}. The player \nameref{ch:basic moves} are on page \pageref{ch:basic moves}. The  \nameref{ch:playbooks} are here \pageref{ch:playbooks}:
If you have crossed over from a Sprawl Game, you will also want to look at \nameref{sec: the sprawl}}

This first chapter will introduce the basic concepts of the game, what characters, stats and the other core mechanics are and how to use them. The next will introduce the Basic Moves, moves that all player characters have that the set the tone and pace of the game. Then we'll look at game setup, and following that the individual playbooks, so that each player has a unique archetype to play to, play against and create headaches for everyone else. Don't say "Zero does", say "I do".

\section{Stats} \label{sec: Stats}
Every character has six stats which represent their raw ability in different spheres of the world. As you look at them, you'll see areas where they might overlap. This is fine, just use what the triggered move demands for your character in that situation.

\begin{itemize}
	\item \smallcaps{Cool} to remain calm and focused in stressful situations
	\item \smallcaps{edge} to draw on your street smarts, street rep or dark side
	\item \smallcaps{Meat} use your physical talents without cyberware to get stuff done
	\item \smallcaps{Mind} to think your way around a problem with sheer intelligence, lateral thinking or obscure knowledge
	\item \smallcaps{style} to handle a situation with charisma, presence or raw sex appeal
	\item \smallcaps{synth} to interface seamlessly with technology
\end{itemize}

Each of these stats varies between -1 and +2 to indicate how well that specific character acts in that sphere. The higher the rating, the more competent you are.  These Stats are the same as in the Sprawl. If you get \smallcaps{take +1 forward} than you can also add that +1 onto the total for the next roll you make.

\section{ Core mechanics} \label{sec: core mechanics}
\subsection{Roll Dice}	\label{sec: roll dice}
You'll see the instruction to \smallcaps{roll+stat} quite a lot in the rules. This simply means roll two six sided dice and add them and the stat together. As a general rule getting ten or above (10+) is a strong hit  and getting seven to nine inclusive (7-9) is a weak hit. You get what you want, but there's complications. Getting below six (6-) is a miss. You might not get what you want, or if you do, it's only because it sets the MC up to tell a new bit of the story. That is then called the Mc making a move.

\subsection{Making moves} \label{sec: making moves}
Moves are specific set pieces in the genre fiction. They typically come with a trigger, a roll for someone to make, and a range of results. Nearly always, they are powerful things you can do as a player (or MC) to shape the fiction. You can definetly try and guide the story towards a situation where a move you want to use triggers, but the move must trigger in the fiction before dice hit the table. Some moves are called Basic Moves and can be used by any player character. Others are specific to playbooks.

An example: 
Jokero the Trader has just caught Greendog raiding his bins for unsold, out of date food. \\
Jokero: I've had three break-ins the last week and I've had it with these punks. I grab my SchorchTorch Hygenieator 3000, stand above the bin pit and aim down. "Oi, nedstain, where's the pallet of steak you stole last week? Better answer quick matey, or you'll be served up very well done to the meat wagon."\\
MC: "Are you bluffing?"\\
Jokero: "Nah. A trader lives by his word."\\
MC: "Right we're playing hardball then, roll +edge."\\
"Play Hardball" is the move for threats backed up by the threat of real violence. If Jokero was bluffing, it would trigger a different move like "Fast Talk" instead. Poor Greendog.\\

\subsection{Experience} \label{sec: experience}
Experience measures how entangled you are in the world, how much you've achieved and how it has left its mark on your character. Every time you \smallcaps{mark XP} it goes on your character sheet playbook. To stay compatible with the sprawl, each time you mark ten experience you'll choose a new advance for your character. The advances you can choose are listed in your character's playbook and include options like raising a stat or choosing a move from a different playbook.

\subsection{MC moves} \label{sec: intro MC Moves}
The MC makes moves based on triggers too. The triggers are a little different though: The MC makes a move when a player misses their move, when the fiction demands it and when the players are waiting for something to happen (around a table, that's tends to be when the conversation stalls and everyone looks at the MC). A full list of the MC moves can be found in \nameref{sec: mcmoves}. When the MC makes their move they may make it a soft move, where the players get a chance to avoid bad consequences, or a hard move, where the consequences happen as they say it. The MC move might appear to unrelated to what you failed at. It does not matter, as long as it moves the fiction along and is interesting.
The MC is also obligated to make hard moves as the fiction demands. Stand in the open firing a pistol at Corp Sec snipers, the fiction demands you get shot, maybe in the leg if the MC is feeling merciful or just interested who'll come and rescue your stupid arse. That said, the MC is not out to kill you.\footnote{in this case, hopefully a previous move would have been "tell the consequences and ask", where they remind you that standing in the open taking potshots at professional snipers is something your character would know is dumb. But maybe you need to buy getaway time for someone else. Man, they'll owe you a big favor.} They are out to make the garish, chrome and neon and dirt encrusted world of Cyber\_Peripherals feel real. They are out to challenge your characters so we can all see how they respond and develop. They are here to find out what happens.

\subsection{Agenda and Principles} \label{sec: intro agenda and princ}
The Agenda are the things the MC must do. They're a damn good guide for players too.
\begin{itemize}
	\item Play to find out what happens
	\item Make the world dirty, shiny, high-tech and unequal
	\item Don't waste your players time.
	\item Entangle the characters with the world.
\end{itemize}

If you are in doubt, do something that fulfills the agenda. The easiest way to do this consistently is the more detailed rules the MC must follow called the Principles:
\begin{itemize}
	\myitem chrome everything, then make it dirty
	\myitem make everything corporate. make everything reused.
	\myitem start with the vertical
	\myitem ask questions about the everyday. 

	\myitem address the characters, not the players
	\myitem ask loaded questions and incorporate the answers

	\myitem name everyone, make them rational
	\myitem treat your NPCs like disposable assets
	\myitemend build shifting, unstable communities
 \end{itemize}

\subsection{Tags}
A tag is a word which describes a significant fictional characteristic of something in the game. It's a quick, semi-formal shorthand for something interesting about an object, person, gang, vehicle ect. They can be positive or negative, or might be a mixed bag. For example, a '+flashy' jacket might a good bribe for a tasteless gambler, but the MC might call up the '+flashy' jacket as the reason you were noticed after failing a roll. A weapon with '+hair-trigger' might be justification for getting that first shot off, but might also be an MC follow-up move if you drop your gun.

The purpose of tags is to condense the description of things to the parts that might matter for the story. They also provide inspiration and invite different moves for players and the MC. An '+ex-military' gang is going to behave differently to a '+scavengers' gang, and an '+ex-military +scavengers' gang has told you a lot about the world in only two words. The suggestiveness of combinations of tags makes them especially useful to help improvisation at the table.

Some tags have explicit impacts on the game mechanics as well as fiction (for example +ap weapons ignore armour) but most impact on the fiction.

\subsection{Favours}
Favours are introduced from Urban Shadows. In the shadowy slums and favelas and encrusted fungal brackets on the great arcologies, Cred is useful, important even. Inside the community, \smallcaps{favours} are just as important. Favours between characters tie them together, often for more than just paying the favour off. Being owed favours lets you punch a little above your weight. Owing favours is a sign that others trust you to pay them back. Unless you don't, in which case remember, the street finds its own uses for things.

\subsection{Gangs}
Gangs are introduced from Apocalypse World. The Sprawl is all about hard-bitten individuals who chase the mission, creds and their directives. Cyber\_Peripherals is all about communities, and sometimes bits of those communities work together. The gangs section of the rulebook has explicit mechanics for handling gang on gang conflict easily, but mostly gangs are about characters, the stories that unfold and the additional fictional positioning. You can literally have characters in three places at once. Handy.

\subsection{Fictional Positioning}
Some moves, tags or equipment don't have numerical effects in the game mechanics. Instead they give the characters fictional positioning, the option to undertake certain kinds of action. You can't give somebody a lift if you haven't got a vehicle. You can't shoot somebody unless you have a gun. You can't fix somebody's roof unless you have the materials, tools and a way to get up there safely. But maybe, with the right combination of equipment, cyberwear and help from someone giving you a boost, you can. No move triggered, no dice needed.

Sometimes fictional positioning is used to make the ground less steady. The trader accepted a '+blackmarket' shipment. That means the MC has a justification, almost a responsibility, to find out what that means for the story, by unleashing a couple of cybered-up custom agents. Someone's rolled a miss, and has a '+disloyal' gang. Well, One-Eyed Kratus has been complaining in fiction for a while now, perhaps it's time to challenge for gang leadership? 

You don't win a game like this, but if a player sets up their character to run a gang with the '+disloyal' tag , they might as well be saying "I want a story where a brutal leadership challenge happens.". Players and MCs both, giving players what they are asking for is a good thing for the game. Player's -  make your interests as explicit as you want. MCs- use them, incorporate them, even aim at them. Make sure you've all got the same expectations going in. 



%%
% Start the main matter (normal chapters)
\mainmatter

\include{_Story}
\chapter{Basic Moves} \label{ch:basic moves}

\subsection{Act under Pressure (cool)} \label{move: act under pressure}
When you race against the clock, act while in danger or act to avoid danger, \smallcaps{roll+cool}
\begin{itemize}
	\item On a 10+ you do it, no problem.
	\item On a 7-9 you do it but flinch. The MC will offer you a worse outcome, hard bargain, or ugly choice
	\item On a 6- you fail to do it. Ask the MC what the repercussions are.
\end{itemize}
This move is the same in the Sprawl. It's the move that covers situations where the outcome is uncertain but you haven't got a better move to make.

\subsection{Read the Street (edge)} \label{move: read the street}
When you read a charged situation \smallcaps{roll+edge}
\begin{itemize}
	\item On a 10+ ask up the three listed questions at any time during the scene
	\item On a 7-9+ ask one listed question
	\item On a 6- ask one listed question anyway, but be prepared for the worst.
	\begin{itemize}
		\myitem Where's my best escape route / way in/ way past?
		\myitem Where's the profit here?
		\myitem Which enemy is the biggest threat?
		\myitem What should I be on the lookout for
		\myitem How can I avoid trouble/ hide here?
		\myitemend Who or what is in control here?
	\end{itemize}
\end{itemize}
This move is a modified mixup from the Sprawl and from Apocalpyse World.\footnote{interestingly, Urban Shadow's does not have a basic move dedicated to assessing a sitch, only people}
 It's the move you use to get information. The MC should be generous and truthful with answers. Confident players do interesting things. 

\subsection{Figure Someone Out (mind)} \label{move: figure someone out}
When you try to figure someone out \smallcaps{roll+mind}.
\begin{itemize}
	\item On a 10+ Ask two listed questions
	\item On a 7-9+ Ask two listed questions, and they get to ask you one.
	\item On a 6- Ask one listed question, and they get to ask you two.
	\begin{itemize}
		\myitem Who is pulling your strings?
		\myitem What's your beef with ...?
		\myitem What are your hoping to get from ...?
		\myitem How could I get you to ...?
		\myitem What do you worry might happen?
		\myitemend How could I make you owe me a favour?
	\end{itemize}
\end{itemize}
This move is a modified version from Urban Shadows. \footnote{in parrallel to read the street, the Sprawl does not have a basic move for reading people. Presumably to keep the chromed up killers from empathy :) }
The you is directed to the character, but the owner must reply reasonably truthfully. This move can be carried out at range. In that case, the reflected questions might be clues, dna traces, search metadata ect that the player character left behind.


\subsection{Play Hardball(edge)} \label{move: play hardball}
When you get in someone's face threatening violence you intend to carry through \smallcaps{roll+edge}
\begin{itemize}
	\item On a 10+ NPCs do what you want. PCs choose: do what you want, or suffer the established consequences
	\item On a 7-9 for NPCs, the MC chooses one:
		\begin{itemize}
		\myitem they attempt to remove you as a threat, but not before suffering the established consequences.
		\myitem they do it, but they want revenge. Add them as a Threat.
		\myitemend they do it, but want real payback. Owe them a \smallcaps{ Favour}.
		\end{itemize}
		PCs choose: do what you want, or suffer the established consequences. They get +1 forward to act against you.
	\item On a 6- it all goes to shit. Look at how much the MC is grinning.
\end{itemize}
This  move is a modified version from the Sprawl. The corporate clocks don't apply here but favours do. 

\subsection{Fast Talk (style)} \label{move: fast talk}
When you try to convince an NPC to do what you want with promises, lies or bluster \smallcaps {roll+style}. If you call in a favour they owe you before rolling \smallcaps{add +3 to roll}
\begin{itemize} 
	\item On a 10+ NPCs do what you want. 
	\item On a 7-9 NPCS do it but they modify the terms or you owe them a \smallcaps{ Favour}. 
	\item On a 6-  they can't. They might tell you why, or maybe you're just interrupted...
\end{itemize}
This move is a mashup from the Sprawl and Urban Shadows. If you want to persuade a PC, call in a favour or offer one to them.
When you call in a favour to get the +3, make sure you explain how you've done that in fiction, whether through explicit appeals to their sense of honour or dark threats about hidden secrets.

\subsection{Mix it Up (meat)} \label{move: mix it up}
When you use violence to seize control of an objective, state that objective and \smallcaps{roll+meat}
\begin{itemize}
	\item On a 10+ you achieve your objective.
	\item On a 7-9 you achieve your objective but choose two.
		\begin{itemize}
		\myitem you leave something behind (MC to detail)
		\myitem you take harm as established by the fiction
		\myitem an ally takes harm as established by the fiction
		\myitemend something of value breaks
		\end{itemize}
	\item On a 6- you don't achieve your objective. Pray the MC offers you a hard bargain.
\end{itemize}

This move is a modified version from the Sprawl. The objective is very rarely "kill everyone". Those mad-dog types tend not to last in the Peripherals. It might be "recover the drugs packet.", "Impress and terrify the merchant.", "steal the drone", "escape the ambush." or similar. Dealing damage is more of a side effect than the aim. You can't tailor the objective to avoid the consequence of your choice on a 7-9 result. 

\subsection{Suffer Harm} \label{move: suffer harm}
When you suffer harm, (even 0-harm or s-harm) then reduce the harm by the level of your armour (if any), fill in the segments on your harm clock equal to the remaining harm and \smallcaps{roll+harm taken}. Try and get a low result.
\begin{itemize}
	\item On a 10+ choose 1:
		\begin{itemize}
		\myitem you're out of action: unconscious, trapped, incoherent or panicked.
		\myitem take the full harm of the attack, before it was reduced by armour. If you already did, take +1 harm.
		\myitem lose the use of a piece of cyberwear till you can get it repaired (you choose).
		\myitemend lose a body part (arm, leg, eye).
		\end{itemize}
	\item On 7-9 the MC will choose 1:
		\begin{itemize}
		\myitem you lose your footing
		\myitem you lose your grip on whatever you are holding
		\myitem you lose track of someone or something you're attending to
		\myitemend someone gets the drop on you
		\end{itemize}
	\item On a 6- you grit your teeth, but nothing worse happens to you. Yet.
\end{itemize}

This move is straight from the Sprawl. Note that the dice results are reversed; low is successful and high is complicated.

\section{Favour Moves} \label{sec: Favour Moves}
These a specialist form of basic move. Everyone has them, and they are focused on the additional game mechanic for cast-iron favours adopted from Urban Shadows. They won't come up as often as the basic moves, but you'll see them multiple times a session. 

\subsection{Help/Interfere}
When you help/interfere with another PCs move in the fiction, \smallcaps{roll+favours they owe you} (to a max of 3+)
\begin{itemize}
	\item On a 10+ you can add +1 or -2 to their roll as you wish
	\item On a 7-9 you can add +1 or -2 to their roll as you wish, but you are exposed to complications of their move.
	\item On a 6- you are ineffectual, distracted or make the situation worse.
\end{itemize}
This is a original move. You can't stack multiple help/interfere moves.

\subsection{ Do someone a favour.}
If you do somebody a favour, they owe you a favour. If it is a big favour (like saving their  kid from a burning building), maybe they owe you two. If you are unlikely to see them again, you're unlikely to get the favour back.

\subsection{Pay back a favour}
\label{sub: pay back a favour}
When you demand someone pays back a favour, remind them why you owe you and:
\begin{itemize}
	\item Make a PC:
	\begin{itemize}
		\myitem do you a favour at moderate cost.
		\myitem help/interfere as you ask
		\myitem answer a question honestly
		\myitem cancel a favour somebody owes them
		\myitemend transfer ownership of a favour somebody owes them to you.
	\end{itemize}
	\item Make an NPC
	\begin{itemize} 
		\myitem answer a question honestly about their organisation
		\myitem introduce you to a powerful member of their organisation
		\myitem give you a useful and worthy gift without cost
		\myitem give you +3 to fast talk them (see \nameref{move: fast talk})
		\myitem cancel a favour somebody owes them
		\myitemend transfer ownership of a favour somebody owes them to you.
	\end{itemize}
\end{itemize}

This is barely modified from Urban Shadows. It's a quite codified approach to commonsense bartering that humans have managed since before fire. Go by the fiction first, and if two players agree a favour between them is paid off, it's paid off. They might even want to keep it so that each owe the other a favour to use on help/interfere rolls.

\subsection{Put off a debt (style)}
When you refuse to pay back a favour you owe when asked, \smallcaps{roll+style}
\begin{itemize}
	\item On a 10+ you weasel out of the current situation, but you still owe them a favour
	\item On a 7-9 weasel out of it for now but you choose one:
		\begin{itemize}
		\myitem{You owe them an additional debt}
		\myitem{It leaks online. Take the +untrustworthy tag until you make it right}
		\myitemend{Expect hassle from their organization or contacts}
		\end{itemize}
	\item On a 6- you can't avoid the noose. Honour your debt or the person owed chooses:
		\begin{itemize}
		\myitem{they pick two from the list above}
		\myitemend{you loose all debts owed to you}
		\end{itemize}
\end{itemize}

This move is heavily modified from Urban Shadows. Sometimes you can't pay a favour back right now. Sometimes, the 'reasonable' thing they are asking for is more than you want to pay right now. This doesn't get you out of the favour, but it might let you put it off for a bit. And if you end up paying a bit of interest or having to work off a reputation, well, that's for future you to deal with. The only way to get a favour canceled completely is to have someone else get you out of it it via \nameref{sub: pay back a favour}. 


\section{Max moves}
Like basic moves, these are open to all. They probably won't come up all that often but just in case...

\subsection{Exchange bodily fluids}
When you exchange bodily fluids with an NPC take 1xp.\footnote{Yes this means sex, but can also mean giving someone a blood transfusion, crying together or assisting at the birth. The MC is encouraged to create painful complications for a player that tries to farm xp this way whether by claiming they are a orgy specialist sex-bot or by selling their blood and claiming it  as a transfusion. Advancing this way is funny the first time, but trying to claim more xp then all the other players combined gets old fast. }
When you exchange bodily fluids with a PC stare at each other for three seconds, then both say if you are guarded or vulnerable. 
If you both say guarded, nothing more happens. If you both say vulnerable, take 1Xp each. If one of you says guarded and the other vulnerable, then the guarded one takes 2Xp.

\subsection{Acquire Agricultural Property (meat)}
When you hit 0000 on your Harm Clock, \smallcaps{roll +meat}
\begin{itemize}
	\item On a 10+ you survive until the medics arrive
	\item On a 7-9 you survive at a cost. Pick one:
		\begin{itemize}
		\myitem substandard treatment (-1 to a stat)
		\myitem cyberware damage (give one piece of cyberwear a negative tag)
		\myitem cleaned out. (loose all but one thing you own)
		\myitemend research division (+owned and change to a suitable sprawl playbook)
		\end{itemize}
	\item On a 6- you bleed out on the street. Sucks.
\end{itemize}

This is slightly modified, mostly to account for why a Corp would be interested in rebuilding slumscum like you. For the MC, any option is an opportunity to introduce complications. Who treats the character and why? Hook them with contracts, threats, implants, addictions, antidotes or a nice list of favours owed. Nothing is free.

\subsection{Go under the knife (cred)}
When you have new cyberware installed by a street doctor, \smallcaps{roll+cred spent} (max of +2)
\begin{itemize}
	\item the operation was a success
	\item The cyberware doesn't work as advertised. choose one  \footnote{DESIGNER NOTE. RETURN TO THIS ONCE Negative tags for cyberware are sorted out}
	\begin{itemize}
		\myitem +damaging: sometimes it hurts like hell and eventually it will do permanent nerve damage
		\myitem + hardware decay: it works now, but it's just a matter of time
		\myitem + substandard: it works but not as well as it should
		\myitemend +unreliable: sometimes it doesn't work.
	\end{itemize}
	\item there have been ... complications
\end{itemize}

This move is just as it is in the Sprawl. Obviously, you're going to need to find a back alley doc, ripper or bonesaw to carry out the operation. Using go under the knife to acquire cyberware is discussed in \nameref{ch:cyberware}. Fair prices for gear (including cyberwear) are listed in \nameref{ch:assets}.
There's no option for corporate sponsorship because frankly, why would they be interested in you? Come back when you're a pro with a reputation, or at least a Sprawl playbook.

\chapter{Preparing to play} \label{ch:preparing to play}

UNFINISHED. to be fleshed out in more detail.\\

Step 0: Define the corporations (or import them from your sprawl game)\\
Step 1: Choose a playbook. Unique playbooks in this case, you're the archetype of your community.\\
Step 2: Name and describe your character.\\
Step 3: Assign Stats
Step 4: Choose Cyberware
Step 5: Choose playbook Moves
Step 6: Choose gear
Step 7: Build your community

\section{install Sprawl drivers?} \label{sec: the sprawl}

If you don't intend for the game world to overlap with your sprawl game you can skip this section. \\

The game is designed to be compatible, with the sprawl, but really, your ultra-competent leatherclad assassin and Kimmy the Waif move in pretty different worlds. In essence, when you Hit the Streets, you are asking around the Peripherals. When you declare a contact, that contact might be a hot-shot VTOL pilot, but they might be Abrahim the Worm, a nobody in Hacker circles, but the guy to go to get a phone unlocked delicately. When your Killer powers down after a brutal rampage, someone has to hose the guts off and check the wires ain't worked loose. Some characters go home to sleep, others need a week in a ambrosia tank. Who's the doc?
Welcome to the Peripherals. 

There were two inspirations behind this game. I've spent enough time working in development engineering and living in places where a smartphone was easier to come by than clean food to be interested in the lopsided tech of developing slums as reality chases past cyberpunk. Things like the favour-economy, where a cousin in the police makes an arrest record fall down the back of the cabinet but later on mentions his daughter would like to join your English school.  The same school being run by a friend who's an accountant by day, but you knew someone who could help get her (perfectly correct) paperwork signed off by a corrupt official. The other inspiration was the design space left by the Sprawl's excellent mission focused structure. It does what it does with a razor focus, but over time my players were interested in developing their characters non-business interactions with the world. There's also the matter of recurring NPCs in the sprawl game. It can be a fun change in pace 

So, the game. If you start with a Sprawl campaign, you've got a lot of the style choices, technologies, social problems ect already agreed. It makes sense for the same mega-corps to be present in the background, but makes much less sense for them to take a personal interest in the game. For that reason, the corporate clocks are not active by default. Stats are the same, and if a player wants to use an established NPC reasonable equipment that we've seen the NPC with should be included. If you want to play a Sprawl character in the periphery, use the "The Pro" playbook. You lose some moves because you're not on a mission, but you keep the stats, some moves, and some corporate interest. You get a hideaway, a mysterious reputation and the the ability to make worlds collide.

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Playbooks} \label{ch:playbooks}

Want to crosswire devices and contacts? Try the Breaker\\
Want to bring mates and muscle? Try the Goon\\
Want your own little store to own? Try the Trader\\
Want to be a diploma from the school of life? Try the Prole\\
Want to confront injustice head on? Try the Outcast\\
Want to tie different stories together? Try the Veteran\\
Want to explore the power of a mega-corp? Try the NGOwned\\
Want to explore relationships without power? Try the Waif\\ 
Want to terrify everyone else? Try the Bonesaw\\



%%%%%%%%%%%%%%%%%%%%%%%%%
\include{BreakerStory}
\section{Breaker} \label{sec: Breaker}

You aren't a hacker. Cyberspace is for tourism, not to live in. But when someone comes to you with a cuffed phone, a tagged handbag or an implant that has locked following warranty expiration, you're the person who gives them back their stuff. For a values of theirs, and a value of gives. 

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something historical, something techno, something weirdly common, something edible
\\ \smallcaps{eyes}: bloodshot, focused, distant, artificial, hidden
\\ \smallcaps{face}: rash, artificially stable, moody, elongated, passionate, modest
\\ \smallcaps{body}: pale, steely, freckled, lined, dimpled, bright
\\ \smallcaps{skin}: black, tattooed, hard, bright, with large pores, fair
\\ \smallcaps{wraps}: square, light, violent,steady, innocent, painstaking, protruding, red, slovenly, colorful
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
2&0&0&-1&1&1\\
1&1&-1&0&2&1\\
1&-1&0&0&1&2\\
\bottomrule
\end{tabular}
\end{table}

Start with one chrome, a workshop and everybody at the table owes you a favour.

\subsection{Breaker's Workshop}
You have a workshop. Choose three good tags and one bad one

\begin{multicols}{2}
\begin{itemize}
\item Gene sequencer
\item quantum decryptor
\item boxes of electronics
\item crude AI assistant
\item environmental isolation systems
\item mobile workshop
\item micro-manipulators
\item fast lane comms access
\myitem cramped
\myitem marked
\myitem unreliable
\myitemend infested
\end{itemize}
\end{multicols}

\subsection{Crack Knuckles}
When you get to work on a manufactured object \smallcaps{roll+mind}
\begin{itemize}
\item On a 10+ ask three
	\begin{itemize}
	\myitem What is hidden here?
	\myitem How can I repair this?
	\myitem Who's looking for this?
	\myitemend What's a good alternative use for this?
	\end{itemize}
\item On a 7-9 ask one
\item On a 6- ask one, but you'll damage the object
\end{itemize}

\subsection{Latest model brain}
When you pitch your services to someone \smallcaps{Roll+style}
\begin{itemize}
\item On a 10+ they're impressed and offer you a paid job
\item On a 7-9 they're impressed and offer you a job paid in favours
\item On a 6- you fluff it. MC's  move...
\end{itemize}

\subsection{Try this number}
If you can't (or won't) deal with something, you probably know who can. Give the customer a number and \smallcaps{roll+edge}
\begin{itemize}
\item On a 10+ it's who they need. Both will owe you a favour
\item On a 7-9 it's who the customer needs need but choose one:
	\begin{itemize}
	\myitem they're expensive
	\myitem you'll owe them a favour
	\myitemend they have a grudge against another player
	\end{itemize}
\item On a 6- they're dead, missing or worse. Shit!
\end{itemize}

\subsection{Red hot networker}
When you explore a new area or market for new clients, opportunities or profit \smallcaps{mark XP}

\subsection{How's tricks?}
You've got an apprentice/partner/assistant of the opposite sex. At start of session \smallcaps{roll+mind} for background gigs.
\begin{itemize}
\item On a 10+ You are in profit. Take three creds.
\item On a 7-9 Take two credit but one of the following
	\begin{itemize}
	\myitem Corporate Security heat
	\myitem Protection money is due
	\myitemend You've got another player in the shit.
	\end{itemize}
\item On a 6- take one credit and the MC will choose one for you.
\end{itemize}

\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Finger probes
\item Eye scanner
\item Comm link
\item Lockpick implant
\item something
\item something
\item something
\item something
\item something
\end{itemize}
\end{multicols}

%%%%%%%%%%%%%%%%%%%%%%%%%
\include{GoonStory}
\section{Goon} \label{sec:Goon}

Society is broken, and you know it. It's a thankless task, but you and your mates are fighting to make a better future, something that is bigger than any one of you. Know what else is bigger than an individual? Your gang. After all, if you are fighting for your little vision of the future, you're going to need to break a few eggs.

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something historical, something backwards , something aspirational, something political
\\ \smallcaps{eyes}: beady, cautious, hot-headed, polite, large, squinty
\\ \smallcaps{face}:  seamed, pointed chin, loose, tattooed, muscular, weak chin
\\ \smallcaps{body}: limp, hourglass, chunky, sleek, 
\\ \smallcaps{skin}: dull, baby-soft, tattooed, mottled, creamy, dark
\\ \smallcaps{wraps}: flashy, ferocious, goatee, shaved, painted, tacky
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
0&  0&  2& 1&1&-1\\
0&  -1& 1& 2&1&0\\
-1&  1& 1& 1&2&0\\
\bottomrule
\end{tabular}
\end{table}

Start with two chrome and a small gang. Answer these questions: "Who had your back when you needed it? Who slept with someone you  wanted? Who is the go-to when stuff goes wrong? What marks the edges of your territory?"

\subsection{Vigilantes}
At start of session \smallcaps{roll + coll} on behalf of your territory.
\begin{itemize}
\item On a 10+:  It is cool. Someone has got something you might like.
\item On a 7-9: Petty trouble. Who did you rough up? Who owes you a favour now?
\item On a 6-: Storms coming. Pick two:	
	\begin{itemize}
		\myitem corporate security sweep
		\myitem corporate developments want land
		\myitem yakuzas moving in
		\myitemend environmental disaster
	\end{itemize}
\end{itemize}

\subsection{Heavies}
Your Gang starts at medium sized and has a piece of heavy weaponry. \footnote{ADD Xrefs to gang size section and weaponry list}
When you need to recruit \smallcaps{roll+meat}
\begin{itemize} 
\item On a 10+ you are back up to full strength.
\item On a 7-9 you are back up to strength but you owe some favours. Ask the MC.
\item On a 6- you are back to strength, but someone's a traitor.
\end{itemize}

\subsection{Patch you up}
When you perform first aid on an NPC, espcially one of your gang, \smallcaps{mark xp}. 
When you perform first aid on a player, they heal 1-3 (your choice), and you \smallcaps{mark xp}. 
Modify favours if the situation calls for it.

\subsection{Post traumatic enthusiasm}
You've got something that stretches your grin. Choose one: fire / grenades / demolitions / orbtillery\footnote{orbital weapons. How the hell did you get access to that?}.
When indulging \smallcaps{rol+coll} 
\begin{itemize}
\item On a 10+ choose three
\item On a 7-9 choose two
\item On a 6- choose one:
	\begin{itemize}
	\myitem the timing is perfect
	\myitem the effect is devastating
	\myitem the precision is surgical
	\myitemend you don't stay to watch
	\end{itemize}
\end{itemize}

\subsection{Street politics}
When you and your gang reinforce your bond through ritual \smallcaps{roll+meat}
\begin{itemize}
\item On a 10+ take \smallcaps{+1 forward} for you and your gang
\item On a 7-9+ take \smallcaps{+1 forward} for you OR your gang
\item On a  6- there's ideological disagreement. You'll need to have it out now or later (MC to take note)
\end{itemize}

\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item dermal plates
\item muscle pak
\item weapon hardpoint
\item weapon holdout
\item electoo tats
\item RI pieces
\item artisan liver
\item limb stump
\item something
\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%

\include{TraderStory}
\section{Trader} \label{sec:Trader}

Capitalism is dead, long live Corpocracy! Buy and trade and exchange favours, old as humanity and as hardwired as that market ticker aug in your left eyeball. Thing is, is the market is a monster. It eats profit and shits out marginal returns and the occasional payoff. Corporations don't like that, it's why the Zaibatsu's declare war on free trade. Well, you ain't about to take that from the Man. You'll buy and sell and provide storage and shipping points, just like your granddaddy cubed did on a junk sailing into Hoi An.

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something international, something techno, some extinct brand, some cypto-currency
\\ \smallcaps{eyes}: mild, languid, candid, moody, cool-headed, resigned
\\ \smallcaps{face}: lined, pallid, Greek, flared, chalky
\\ \smallcaps{body}: thin, comfy, pot-bellied, terrifying, luxuriant, bald
\\ \smallcaps{skin}: pale, wrinkled; neckbeard, delicate, supple, clipped, orange
\\ \smallcaps{wraps}: symmetrical, ribbed, professional, knit, savvy, adorable
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
2&1&1&0&0&-1\\
1&2&1&0&-1&0\\
1&1&2&-1&0&0\\
\bottomrule
\end{tabular}
\end{table}

Start with one chrome, a tradesite and a couple of staff.

\subsection{Tradesite}
You're doing ok. Long hours but decent money. Is your site mostly physical or unreal? Pick a main stock and two sidelines.
Tell the rest of the table what you stock, it'd be common knowledge and there might be some nice worldbuilding that comes out of it.
 You Also have a couple of reasonble trustworthy staff. How do they exemplify your stock? One owes you a favour.

\begin{multicols}{3}
\begin{itemize}
\item sex
\item highs/narco
\item Spirits/tranqs
\item wholsesale data
\item cheap foodstuffs
\item nostalgic junk like books
\item currency transfers
\item souvenirs
\item live animals, plants
\item fashion/cosmetics
\item tools/chemicals
\item second hand goods
\item vehicles
\item consumer gadgets, media and medical
\item sports equipment
\item gamepads
\item snacks/drinks/bottled air
\item weapons
\end{itemize}
\end{multicols}

\subsection{Know your customer}
You have access to various corpo-credit, source'o'wealth and blacklisting databases. If someone spends at your store or another player brings you a scan of their card, you can dial the card owener up: \smallcaps{roll+edge}
\begin{itemize}
\item On a 10+ You find something juicy blackmail worthy. Hold one favour over them.
\item On a  7-9 There's a pattern or opportunity to pressure them, but the window is closing.
\item On a 6- You ain't the first to look them up, and now corpsec want to know why.
\end{itemize}

\subsection{Bite me}
You owe a loanshark big. Until it is paid off they can hit you up for unlimited favours. This has the advantage of focusing the mind. Start with as many credits as you want and 35 cycles grace. \\ When you fail a roll you may reroll but strike the total of the new roll from the 35. When your grace hits zero, the debt comes due. You'll need to payback at least twice what you borrowed. You can take another loan out. You can even take a loan to payoff off the first loan. Just don't let the sharks find out.

\subsection{Always right}
When you flatter a major customer or haggle with a supplier \smallcaps{roll+style}
\begin{itemize}
\item On a 10+ you make +three credit. score!
\item On a 7-9 you make +one credit. See you again!
\item On a 6- you make +three credit, but man are they going to be angry later. Why?
\end{itemize}

\subsection{Store security}
It's a rough neighbourhood but one little piece of it is yours. When you are in your shop \smallcaps{take+1 cool}.
In addition, choose one and add it to your shop.
\begin{multicols}{2}
\begin{itemize}
 \item pop down weapon turrets
\item hotline to corpsec company
\item Logan the security guard
\item Logan the cyber mastiff
\item Nagol the ICE manifestation
\item Everyone, including the regulars, are packing.
\end{itemize}
\end{multicols}{2}

\subsection{Market niche}
When you deal with the corps at high stakes (for you) \smallcaps{mark xp}.


\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Comm link
\item Visor
\item lie detector
\item market feed
\item metal detector
\item something
\item something
\item something
\item something
\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%

\include{ProleStory}
\section{Prole} \label{sec:Prole}

Live to work or work to live? The problem is doing either steady. The gigeconomy favours the multiskilled, and while the meat is weak skillchips are available by the hour. For a fee. Screw that.

You  owe two favours and are owed two favours. If you want it, you also have a beat up vehicle. 

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something historical, something techno, something weirdly common, something edible
\\ \smallcaps{eyes}: fussy, oblong, caustic, persevering, emotionally stable, mean
\ \smallcaps{face}: strong, luminescent, bulbous, black, seamed, translucent
\\ \smallcaps{body}: long fingers, rounded, good, huge, chubby, moustache
\\ \smallcaps{skin}: glowing, musty, flecked, scarred, orange, oily, warm
\\ \smallcaps{wraps}: open-backed, dainty, form-fitting, sensational, pressed, pushup
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
2&0&0&1&1&-1\\
1&0&-1&2&1&0\\
1&-1&0&1&2&0\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Quite a wardrobe}
when you impersonate a corp gig you may have conceivably had held in the past, \smallcaps{roll+style}
\begin{itemize}
\item Your body language is convincing.
\item You'll fool most but there's a telltale. Choose one:
	\begin{itemize}
	\myitem You are the wrong sex/weight/race/ for branding
	\myitem RFID tags in the unifrom are out of date
	\myitemend you can't talk the talk. What are these new TLAs?\footnote{Three Letter Acronyms}
	\end{itemize}
\item It fails and someone is following you/confronts you
\end{itemize}

\subsection{Jacked into all trades}
When you want to fix, build and repurpose something tell the MC what you are aiming for. They'll string together one to four of the below with 'and' or perhaps a merciful 'or'.
MC says: "Yes, but first..."
\begin{itemize}
\item you'll need a workshop
\item you'll need this piece of equipment/toolkit
\item you'll need help from ....
\item it'll take a lot of testing
\item it's going to take time
\item you'll need to make ...
\end{itemize}
Anything major made probably deserves a custom move, and anything that deserves a custom move deserves to be a major bit of work. You can have multiple projects though.

\subsection{Clock off}
When you hit the bars/gym/whatever to blow off steam \smallcaps{roll+meat}
\begin{itemize}
\item On a 10+ you wake up at full health holding two favours. (MC to say who)
\item On a 7-9 you wake up at full health OR hungover but owed two favours
\item It's late, you're hungover and now you owe a favour to ... (MC to say who)
\end{itemize}

\subsection{My other life}
When you join in something creative/artistic that is bigger than just you \smallcaps{roll+style}
\begin{itemize}
\item On a 10+ It's awesome. Describe what it adds to the area. Whilst there you can reroll a failed roll. You can't reroll a reroll.
\item On a 7-9 It's awesome. Describe what it adds to the area.
\item On a 6- It's awesome and goes viral. Now money grabbers are keen to cash in.
\end{itemize}

\subsection{This is Scooter}
When you get another player a gig with you, \smallcaps{mark xp.}\\
When you quit a job in disgust \smallcaps{mark xp.}


\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Tool implant
\item Eye Scanner
\item Productivity drug dispensor
\item muscle pak
\item slot chip frame
\item jack in hardpoint
\item skillwires
\item something
\item something
\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%

\include{OutcastStory}
\section{Outcast} \label{sec:Outcast}

Everyone in the community is an outsider to the shiny world of the rich and corpocratic, but you and your ilk stand outside the community too. You may end up rich and even powerful, but you will never really be accepted. Don't take this playbook if you aren't comfortable with the consequences.

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something monosyllabic; some waste product; something natural; something emotional
\\ \smallcaps{eyes}: drooping, brown-eyed, steely, petite, Roman, bisque
\\ \smallcaps{face}: torpid, coherent, pointed chin, languid, raw, proud
\\ \smallcaps{body}: sunken, alive, thick, blue, windblown, sad, small, quick
\\ \smallcaps{skin}: messy, ample, ink-stained, dry, straggly, red
\\ \smallcaps{wraps}: itch-free, collared, fabric-lined, flouncy, fabulous, fabric-lined, ribbed, pragmatic, strapless, double breasted, bloused, innovative
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style 	& Edge & Cool & Meat & Synth & Mind\\
\midrule
0&0&02&1&-1&1\\
0&-1&1&2&0&1\\
-1&0&1&1&0&2\\
\bottomrule
\end{tabular}
\end{table}

Start with a small gang of outcasts and Being the Other.

\subsection{Being the Other}
What thing about you makes corporates and the community nervous?
Choose 1:
\begin{itemize}
\item built for breeding
\item diseased. contagious or not
\item member of an untouchable, untrustworthy class \footnote{the originator for this is the Barakumin of Japan, but it can be worked in most cultural settings.}
\item taken on a social role that sets you as a person outside society \footnote {the inspiration for this was actually the village vicar (and witch). A pillar of the community, but not one people feel comfortable around.|}
\end{itemize}


\subsection{Watcher}
At the start of the session, \smallcaps{Roll+Mind}
\begin{itemize}
\item On a 10+ you see the coming wave. Say what will change and how that will change the status quo.
\item On a 7-9 say how the current status quo is vulnerable
\item On a 6- say what there will be shortages of, and if there is likely to be riots.
\end{itemize}

\subsection{Small consolations}
Outcasts stick together. When you need something, let your gang know and \smallcaps{roll+cool}
\begin{itemize}
\item On a 10+ you get what you need
\item On a 7-9 you get a reasonable substitute
\item On a 6- you get it, but you owe a couple of favours. MC take note.
\end{itemize}

\subsection{You ain't my cuz}
When you call someone out as a hypocrite or poseur {roll + meat} \footnote{this applies to everyone. Assuming you get to a position they hear your voice, you can call out the president. It is not just limited to fellow outcasts.}
\begin{itemize}
\item On a 10+ they back down, try to appease you or suffer 0-harm. Target chooses.
\item On a 7-9 they back down in the short term.
\item On a 6- the situation escalates
\end{itemize}

\subsection{My people}
Your gang is large (+large) and you are good at talking to them. When you stir them up \smallcaps{roll+mind}
\begin{itemize}
\item On a 10+ choose their emotional state. They'll follow you.
\item On a 7-9 choose their emotional state. They'll follow it out.
\item On a 6- You fail to impress, are challenged or you are interrupted
\end{itemize}

\subsection{No blacks. No dogs. No Irish}\footnote{Designer's note. I am really unsure of this one and its impact on the table. needs testing} 
When you, as a character, interact with an NPC and you, as a player, beckon at the MC, the interaction will ephasises why you are an Outcast. Take an Xp. 
\footnote {The emphasis may not be overt hostility. It could be ignorant questioning, talking to a different player character despite the Outcast trying to talk to you or simple condescension. It could even be outright support for the Outcast, clumsy or helpful.}

\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Autodoc implant
\item loudhailer
\item Cyrpto locker
\item muscle pak
\item memory banks
\item something
\item something
\item something
\item something
\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%

\include{VeteranStory}
\section{Veteran} \label{sec:Veteran}

You are old. Old enough to have fought, before robots and gangers took that job too. You have been in the community a long time, and like anything that sits still long enough here, you play a supporting structural role in how the community works. Some people respect you. Most owe you. All you've got to do it keep it together.

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: some extinct animal; something military, some far-away place; some old media; 
\\ \smallcaps{eyes}: wide-set, impulsive, logical, pleasing, calm, rheumy, steely
\\ \smallcaps{face}: polished, velvety, jutting chin, impulsive, inconsiderate, jowly, thick
\\ \smallcaps{body}: slicked down / slicked back, voluptuous, ringlets, flabby, limp, harrowing
\\ \smallcaps{skin}: tanned, dead, dowdy, shaved, thick, straggly,
\\ \smallcaps{wraps}: zippered, stunning, gypsy, banded, translucent, racerback, rugged, stylish, innovative, fitted, state-of-the-art, spiritual
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
2&0&0&-1&1&1\\
1&1&-1&0&2&1\\
1&-1&0&0&1&2\\
\bottomrule
\end{tabular}
\end{table}

Start with two chrome, one move, owing two favours and being owed two favours. You get to say who owes you.

\subsection{Drop someone's name}
When you drop the name of someone who owes you a favour, \smallcaps{roll+cool}
\begin{itemize}
	\item On a 10+ their name carries weight and opens an opportunity
	\item On a 7+ you get the opportunity you need, but the favour is spent.
	\item On a 6- you overstep. Erase the favour and brace youself.
\end{itemize}

\footnote{This move is barely modified from Urban Shadows basic move. It is useful anywhere you think that persons name will help you get by. You need to mention they owe you a favour though, and imply you could use that favour against the oppostion.}

\subsection{Death Glare}
You've seen these kids grow up. When you pull on that string you pin your target in place and make it very difficult for them to lie.

\subsection{Chess Master}
When you go into a situation expecting trouble \smallcaps{roll+mind}
\begin{itemize}
	\item On a 10+ the MC will say, or ask, where you can expect trouble from. Take \smallcaps{+1 forward} to escaping it.
	\item On a 7-9 the MC will say, or ask, where you can expect trouble from.
	\item On a 6- the MC will say, or ask, where you can expect trouble from, but leave out a critical detail.
\end{itemize}

\subsection{A beautiful ruin}
Your battle scars and cybergear go well together. When you have to totally dominate attention \smallcaps{roll+style}
\begin{itemize} 
	\item On a 10+ you do it.
	\item On a 7-9 to keep their attention will need showy behaviour too
\end{itemize}

\subsection{Fat Old Spider}
When you get someone to the point of owing you three favours, \smallcaps{mark xp}

\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Dermal Plates
\item Crawler chair
\item Hydraulic Claw
\item Weapon Point
\item Aug Scanner
\item Tethered Watcher
\item Dean Man's Switch
\item something
\item something
\end{itemize}
\end{multicols}



%%%%%%%%%%%%%%%%%%%%

\include{NGOwnedStory}
\section{NGOwned} \label{sec:NGOwned}

You looked down from the spire at the heaving heaving jungle and heard a call. Maybe privelaleged guilt; youthful rebellion or an eye for an opportunity. Anyhow, you're here and you're going to help.

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something religious; something emotional; something artistic; something scientific
\\ \smallcaps{eyes}: translucent, painted, seamed, wolfish, veined, florid
\\ \smallcaps{face}: unpopular, sociable, protruding brow bone, lazy, impulsive, precocious
\\ \smallcaps{body}: slouchy, hot, straight, sleek, blemished, pockmarked, thick, crooked
\\ \smallcaps{skin}: clipped, grimy fingernails, plump, yellow, dead, stubby fingers
\\ \smallcaps{wraps}: fluffy, luxuriant, huge, luxuriant, spiky, ink-stained, tunic length, odor-resistant, sophisticated, oversized, girls', preppy
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
2&1&0&1&0-1\\
1&2&0&1&-1&0\\
1&1&-1&2&0&0\\
\bottomrule
\end{tabular}
\end{table}


Start with two moves; a corporate sponsor and a small gang of like minded individuals. Name them. Answer these questions: "Who did you study with in college?", "Who did you sleep with?", "Who is an adrenaline junky?"

\subsection{Bleeding heart}
When you deliver valuable supplies to a community \smallcaps{roll+meat}
\begin{itemize}
	\item On a 10+ choose two
	\item On a 7-9 choose one
		\begin{itemize}
		\myitem It makes a real difference
		\myitem It's great PR
		\myitemend It will scale well
		\end{itemize}
\end{itemize}

\subsection{Family Inc.}
More then just sponsorship, you have a direct line to a close relative in a named mega-corp. When you play that card and that corp is openly involved take \smallcaps{+1 style in that situation}


\subsection{Fieldwork}
When you and your gang s[pilt u[, dig down and figure out an entire community \smallcaps{roll+edge}
\begin{itemize}
	\item On a 10+ choose three
	\item On a 7-9 choose two
	\begin{itemize}
	\myitem You know who are the influencers
	\myitem You know who are the vulnerable
	\myitem You know the pressing secret need
	\myitem You don't feel like you owe the community a favour\footnote{otherwise you do, and members of the community can play on that sense of guilt to demand a mechanical favour from you}. 
	\end{itemize}
\end{itemize}

\subsection{Starving babies}
When you and your gang push a fund raising campaign or stunt \smallcaps{roll+style}
\begin{itemize}
	\item On a 10+ you craft a story about the community that everyone believes and sympathises with.
	\item On a 7-9 the story works to raise money, but you embarrasses someone, or create a story that will never die.
\end{itemize}

\subsection{Free Advertising}
When you and your gang promote your sponsor's interests directly, \smallcaps{mark xp}

\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Empath Glove
\item Auto Doc implant
\item Eye scanners
\item Market Feed
\item Finger Probes
\item something
\item something
\item something
\item something
\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%

\include{WaifStory}
\section{Waif} \label{sec:Waif}

Growing up sucks, but so does being a kid. You're relatively powerless, reliant on blunt-nose adults and still finding your way. At least tech is easy.

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something edible; something monosyllabic; some small animal; something gamer
\\ \smallcaps{eyes}: blunt, moody, cool-headed, jowly, tactful, rheumy
\\ \smallcaps{face}: veined, florid, sharp cheekbones, drooping, bleary, translucent
\\ \smallcaps{body}: bright, harrowing, compact, carved, sturdy, untamed
\\ \smallcaps{skin}: peach, pitted, creamy, glowing, dark, uneven
\\ \smallcaps{wraps}: standard-fit, on trend, latest, stunning, pressed, anatomic, bold, retro, easy-to-maintain, dependable, preppy, high-performance
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
0&2&1&0&1&1\\
0&1&2&-1&2&1\\
-1&1&1&0&1&2\\
\bottomrule
\end{tabular}
\end{table}

Choose two moves, one chrome, one favour owed and one someone owes you. How did you come by that piece of chrome? Why or who installed it in you?

\subsection{Fast Learner}
At the start of the session, say what you've been doing to get by and take a \smallcaps{temporary +1 to an appropriate stat for the rest of the session}. It must be a different stat to last session.

\subsection{Street Rat}
When you are out on the street and it kicks off \smallcaps{roll+edge}
\begin{itemize} 
	\item On a 10+ hold three
	\item On a 7-9 hold two. Spend hold one for one to:
	\begin{itemize}
		\myitem find somewhere to hide
		\myitem spot something worth stealing 
		\myitem realise what somebody wants
	\end{itemize}
\end{itemize}

\subsection{Script Kiddie}
You're addicted to the net. Pay a credit a week or make other arrangements to keep your fast lane access. As long as you are online you can ask the GM for some random fact related to what you are thinking about.

\subsection{F.R.I.E.N.D}
You have an artificial protector, a guardian machine spirit or a battered toybot. It counts as a piece of chrome, activated by \smallcaps{rolling+synth} where it allows you to do something in the fiction.
Choose one: 
	\begin{itemize}
	\item Protective: can be used as a +1 Armour
	\item Hacker: can be used to subvert technology
	\item Dangerous: can be used as a weapon
	\item Transformer: choose two from the next set
	\end{itemize}
Choose one: 
	\begin{itemize}
	\item Big
	\item Small
	\item Incorpreal
	\item Intimidating
	\end{itemize}
Choose one: 
	\begin{itemize}
	\item Jealous
	\item Slow
	\item Fragile
	\item Stolen
	\end{itemize}

\subsection{Feeling Empty}
When you steal something and consume it alone, you can ask the MC what sort of meal any two characters may have shared in the past. Then \smallcaps{mark xp}

\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Cherubim Wings
\item Implanted tail/limb
\item Memory Banks
\item Pheromone spray
\item Cyber ears
\item Courier pouch
\item Poison Spur
\item Climbing Spurs
\item something
\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%


\include{BonesawStory}
\section{Bonesaw} \label{sec:Bonesaw}

There's lots of reasons to be a Ripper Doc. Maybe you saved some drunk's life and got off on the thrill. Maybe your aunt instructed you in the secret rituals. Maybe you really like cybergear and you read the instruction manual real carefully. Anyhow, they give you creds to risk their lives. Ain't that cool?

\marginnote{
Choose as many as you need:
\\ \smallcaps{name}: something aspirational; something latin; something backwards; something artistic 
\\ \smallcaps{eyes}: pensive, incisive, resigned, courteous, sedate, independent
\\ \smallcaps{face}: rosy, hollow cheeks, tiny, olive, muscular
\\ \smallcaps{body}: weird, plush, lanky, parted, messy, portly
\\ \smallcaps{skin}: bruised, red-rimmed, clear, loose, flawless, tattooed
\\ \smallcaps{wraps}: patchwork, boxy, engineered, on trend, flirty, active, chic, casual, straight, synthetic, constructed of living
}

Choose one row.
\begin{table}[ht]
\centering
\fontfamily{ppl}\selectfont
\begin{tabular}{rrrrrr}
\toprule
Style & Edge & Cool & Meat & Synth & Mind\\
\midrule
0&2&0&-1&1&1\\
0&1&-1&0&2&1\\
-1&1&0&0&1&2\\
\bottomrule
\end{tabular}
\end{table}

Start with a a piece of chrome, a surgery, another move and being owed two favours. 

\subsection{Bonesaw's Sugery}
You have a surgery with an operating theater. Choose three more good tags and one bad one
\footnote{Special stock - choose any piece of chrome from the big list in the rulebook. You always have this in stock. Others are harder to source}
\begin{multicols}{2}
\begin{itemize}
\item Gene sequencer
\item Printer and files
\item Tattoo sets and a rep
\item Ambrosia tanks
\item Special stock 
\item Second special stock
\item Deep brain scanner
\item Mobile workshop
\myitem cramped
\myitem unreliable
\myitem unlicensed
\myitemend owned
\end{itemize}
\end{multicols}

\subsection{Flesh is Cheap}
Your surgery has access to unlimited protein. You can regrow anyone's anything, as long as it is biological and does not count as chrome. Choose a source:
\begin{multicols}{3}
Offal pipe\\
Roach grinder\\
Turd pigs\\
Flesh trees\\
Rag yeast\\
Pigeon loft\\
\end{multicols}

\subsection{Today's Special}
At the start of session \smallcaps{roll+edge}. 
On a hit you have in stock a new, one off piece of cyberwear (salvaged, repaired or crafted)
\begin{itemize} 
	\item On a 10+ pick any from the big list of chrome
	\item On a 7-9 the GM offers a choice of two.
\end{itemize}

\subsection{Potato Head}
When a limb or equivilent gets cut off \smallcaps{roll+synth}
\begin{itemize} 
	\item On a 10+ you can control it remotely
	\item On a 7-9 you can control it, but it will die very soon if not treated.
\end{itemize}

\subsection{A Little Rummage}
When you work on someone on in your surgery\smallcaps{Roll+mind}
\begin{itemize} 
	\item On a 10+ choose 2
	\item On a 7-9 choose 1
	\begin{itemize}
		\myitem Target takes +6 health (including over normal maximum)
		\myitem Remove a negative tag from target's cyberwear
		\myitem You learn something. \smallcaps{Mark xp}
		\myitemend You put something very hard to trace in them (tracker, slow poison, remote bomb, message ect)
	\end{itemize}
	\item On a 6- there have been ... complications
\end{itemize}

\subsection{Chrome}
\begin{multicols}{3}
\begin{itemize}
\item Finger probes
\item Implanted tail/limb
\item Memory Banks
\item Eye scanner
\item Productivity drug dispenser
\item Auto doc implant
\item Poison Spur
\item something
\item something

\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%

\include{TheProStory}
\section{The Pro} \label{sec:The Pro}
You lose some moves because you're not on a mission, but you keep the chrome, stats, some moves, and some corporate interest. You get a hideaway, a mysterious reputation and the the ability to make worlds collide.

For every playbook move you bring from the Sprawl into the Periphery, bring one of the corporate clocks as well. This applies to active moves that grant fiction shaping abilities, not ones that grant a stat increase or an extra piece of chrome. 

\subsection{The Pro's Hideaway}
You have a decent hideout in the Peripheries. It has a bed, food and medicine. Choose three more good tags and one bad one
\begin{multicols}{2}
\begin{itemize}
\item Off grid
\item Enough space for three people 
\item Personal toolkit
\item Holdout weapons locker
\item A true loyal friend
\item Garage with beat up vehicle
\item Robust escape route
\item Holdout net access
\myitem inaccessible
\myitem infested
\myitem environmentally vulnerable
\myitemend known to some
\end{itemize}
\end{multicols}

\subsection{Apply First Aid}
When you treat someone's wounds \smallcaps{Roll+cool}
\begin{itemize} 
	\item On a 10+ If their harm clock is at 2100 or less, reduce their harm by two segments. If their Harm Clock is at more than 2100, reduce their harm by one segment.
	\item On a 7-9 Reduce their harm by one segment. If their Harm Clock is still at more then 2100, they take -1 ongoing until they receive proper medical attention.
\end{itemize}
This move is adopted straight from the Sprawl. You're a professional right? \\
Once a character has been given first aid, more first aid will nto heal them further until they suffer harm again. First aid cannot heal missing body parts or damaged cyberware. To fix these problems, you'll have to make a deal with someone. Trauma Dems are appropriate medical equipment for wounds at 2100 or less. More serious wounds require an EMT kit.

\subsection{Worlds Collide}
When you want to drag another Sprawl character into the Peripherals, \smallcaps{roll+links you have with that character}
\begin{itemize} 
	\item On a 10+ They arrive when you need them
	\item On a 7-9 They arrive at the peak of the action
	\item On a 6- You get someone else. 
\end{itemize}
Yes this means players might end up running two characters at once. Why not?


\chapter{Cyberware} \label{ch:cyberware}
\section{Cyberware List} \label{sec: Cyberware list}

\begin{itemize}

\item Auto doc implant
\item Cherubim Wings
\item Climbing Spurs
\item Courier pouch
\item Comm link
\item Crawler chair
\item Cyrpto locker
\item Cyber ears

\item Dean Man's Switch
\item Dermal Plates
\item Empath Glove
\item Eye scanner
\item Finger probes
\item Hydraulic Claw
\item Implanted tail/limb
\item lie detector
\item Lockpick implant
\item loudhailer
\item Market Feed
\item memory banks
\item metal detector
\item muscle pak
\item Poison Spur
\item Pheromone spray
\item Productivity drug dispenser
\item something
\item Tethered Watcher
\item Tool implant
\item Visor
\item Weapon Point


\item slot chip frame
\item jack in hardpoint
\item skillwires

\end{itemize}

\chapter{Assets} 	\label{ch:assets}
\section {Favours}	\label{sec:favours}
\section {Cred} 	\label{sec:cred}
\section {Gangs}	\label{sec: gangs}
\section {Contacts}	\label{sec: contacts}

\chapter{Advancement}	\label{ch: advancement}
\chapter{The matrix}	\label{ch: the matrix}
\chapter{Running Cyber\_Peripherals}	\label{ch:running the game}
\section{agenda}			\label{sec: agenda}
\section{always say}		\label{sec: always say}
\section{principles}			\label{sec: principles}
\section{moves}			\label{sec: mcmoves}
\section{inflicting harm}		\label{sec:inflicting harm}
\section{countdown clocks}	\label{sec:countdown clocks}
\section{corporations} 		\label{sec: corporations}
\section{threats}			\label{sec: threats}
\section{putting it all together} 	\label{sec: putting it all together}

\chapter{the first session} \label{ch: the first session}

%% ---   ---   ---   ---   ---   
\chapter{Designer Notes}

Rule 1 - No Exceptions\\
Rule 2 - Needs to work for a one shot with strangers at a conference\\
Rule 3 - Evoke, not mimic, the sprawl and cyberpunk\\
Rule 4 - Support the MC\\
Rule 5 - Every mechanical part needs to justify its existence\\
Rule 6 - Every move needs to relate back to theme or the mechanics\\
Rule 7 - No stat substitution moves\\

on Playbooks\\
a) Does this playbook have a niche. Is it overshadowed?\\
b) Is the playbook fun and coherent?\\
c) Does the playbook offer levers for the MC to pull?\\
d) Does the playbook offer a second, different way to play that character?\\

On Moves\\
i) Is the trigger only going to trigger when it is important?\\
ii) does a miss move the sotry forward with something interesting?\\
iii) Does a success?\\
iv) \\

Formatting:\\
Only stats use digits. Hold is spent in one or twos not 1 or 2. Add explanation for hold or choice from list under the first option that uses it.\\
All moves to use the same format of trigger, 10+, 7-9 then 6-\\


%%
% The back matter contains appendices, bibliographies, indices, glossaries, etc.







\backmatter

\bibliography{sample-handout}
\bibliographystyle{plainnat}

\printindex[stuff]

\printindex

\end{document}

